Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-08-29 tex/paper1/paper1.tex
reply to the referee's comments

\begin{abstract}
  The dynamics of regions of the solar corona are investigated using
  AIA 171\AA\ and 193\AA\ data.  It is commonly assumed that coronal
  time-series are well described by the sum of a long time-scale
  background trend plus Gaussian-distributed noise, with some specific
  locations also showing an oscillatory signal.  It is shown that the
  \mFpa\ in all regions follows an approximate \PL\ behaviour.  This
  average behavior is inconsistent with this commonly held assumption.
  The implications of this discovery to the field of coronal
  seismology and automated detections of oscillations is discussed.
  The observed \PL\ \PS\ can be formed by summing a distribution of
  exponentially decaying emission events along the line of sight.
  This is consistent with the idea that the solar atmosphere is heated
  everywhere by small energy deposition events.
\end{abstract}

@@

\section{Introduction}\label{sec:int}
Coronal seismology is the study of oscillatory phenomena in the solar
corona.  First suggested by \cite{1970PASJ...22..341U}, the practice
of coronal seismology attempts to locate oscillatory phenomena in the
solar corona, identify the wave modes present, and then use
theoretical descriptions of those wave modes to infer the physical
conditions of the solar corona.  The practical application of coronal
seismological ideas began in earnest with observations of wave modes
by SOHO/EIT \citep{1998ApJ...501L.217D, 1999SoPh..186..207B} and TRACE
\citep{1999ApJ...520..880A} (see also \cite{lrsp-2005-3},
\cite{2012RSPTA.370.3193D} for more extensive reviews of coronal
seismology).  Since then, many papers have been published describing
oscillatory phenomena in the corona and their interpretation in terms
of theoretically known wave modes.

Oscillatory phenomena in the solar corona are relatively rare, both
spatially and temporally.  Two types of oscillatory motions have
received a lot of attention.  The first is known as a transverse
oscillation, since the loop motion is approximately transverse to the
extent of the loop \citep{1999Sci...285..862N}.  These motions appear
to be triggered by nearby flaring events, and are identified with the
fundamental harmonic of the kink mode of the flux tube that comprises
the coronal loop.  The second type is known as a longitudinal
oscillation, or propagating disturbance (PD).  These waves propogate
along flux tubes, and have been identified as slow mode (MHD)
magneto-acoustic waves (although alternative interpretations do exist
that do not invoke oscillatory phenomena, for example,
\cite{0004-637X-722-2-1013} and \cite{2041-8205-727-2-L37}).

@@

All these detections algorithms, and many detections in the literature
make either the explicit or implicit assumption that the observed
time-series consists of a background trend of some kind and at least
approximately Gaussian-distributed noise.  However, it is shown below,
using data from the Atmospheric Imaging Assembly (AIA)
\cite{2012SoPh..275...17L} on board the Solar Dynamics Observatory
(SDO) \cite{2012SoPh..275....3P}, that time-series of coronal emission
may be better described by other models.  These models have
implications for the practice of coronal seismology, and may be
indicative of the nature of the fundamental energy deposition that
keeps the corona hot.

@@

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
The first contribution to both models $M_{1}$ and $M_{2}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all parts of the solar atmosphere.
Further, \cite{2014AA...563A...8A} show that a \PL\ \PS\ is present in
coronal active region and quiet Sun time-series over the frequency
range 0.01 - 1 mHz, overlapping with the frequency studied in this paper.

>>>>

\begin{abstract}

  {\bf The dynamics of example regions of the solar corona are
  investigated using AIA 171\AA\ and 193\AA\ data. These are examples of
    quiet Sun, coronal loop footpoint, coronal moss and the
    coronal emission above a sunspot.  It is shown that the \mFpa\ in
  these example regions can be described by a power law at lower
  frequencies that tails to flat spectrum at higher frequencies plus a
  Gaussian-shaped contribution that varies depending on the region
  studied. This Fourier spectral shape is in contrast to the commonly
  held assumption that coronal time-series are well described by the
  sum of a long time-scale background trend plus Gaussian-distributed
  noise, with some specific locations also showing an oscillatory
  signal.}  The implications of this discovery to the field of coronal
  seismology and automated detections of oscillations is discussed.
  The observed \PL\ \PS\ can be formed by summing a distribution of
  exponentially decaying emission events along the line of sight.
  This is consistent with the idea that the solar atmosphere is heated
  everywhere by small energy deposition events.
\end{abstract}

@@

\section{Introduction}\label{sec:int}
Coronal seismology is the study of oscillatory phenomena in the solar
corona.  First suggested by \cite{1970PASJ...22..341U}, the practice
of coronal seismology attempts to locate oscillatory phenomena in the
solar corona, identify the wave modes present, and then use
theoretical descriptions of those wave modes to infer the physical
conditions of the solar corona.  The practical application of coronal
seismological ideas began in earnest with observations of wave modes
{\bf described in \cite{1998ApJ...501L.217D} and
  \cite{1999SoPh..186..207B} from data captured by Extreme Ultraviolet
  Telescope (EIT, \citealp{1995SoPh..162..291D}) on board the Solar and Heliospheric
  Observatory (SOHO, \citealp{1995SoPh..162....1D}), and also by
  \citep{1999ApJ...520..880A} using data from the Transition Region
  and Coronal Explorer (TRACE, \citealp{1999SoPh..187..229H}).  Since these initial works,
  many papers have been published describing oscillatory phenomena in
  the corona and their interpretation in terms of theoretically known
  wave modes.  The review articles \cite{lrsp-2005-3} and
  \cite{2012RSPTA.370.3193D} refer to many more articles on both
  observational and theoretical coronal seismology}.

Oscillatory phenomena in the solar corona are relatively rare, both
spatially and temporally.  Two types of oscillatory motions have
received a lot of attention.  The first is known as a transverse
oscillation, since the loop motion is approximately transverse to the
extent of the loop \citep{1999Sci...285..862N}.  These motions appear
to be triggered by nearby flaring events, and are identified with the
fundamental harmonic of the kink mode of the flux tube that comprises
the coronal loop.  The second type is known as a longitudinal
oscillation, or propagating disturbance (PD).  These waves propagate
along flux tubes, and have been identified as slow mode (MHD)
magneto-acoustic waves (although alternative interpretations do exist
that do not invoke oscillatory phenomena, for example,
\cite{0004-637X-722-2-1013} and \cite{2041-8205-727-2-L37}).

@@

All these detections algorithms, and many detections in the literature
make either the explicit or implicit {\bf modeling} assumption that
the observed time-series consists of a background trend of some kind
and at least approximately Gaussian-distributed noise.  {\bf The aim
  of this paper is to test the validity of this assumption principally
  in regions of interest to study of the coronal seismology}.  It is
shown below, using data from the Atmospheric Imaging Assembly (AIA,
\citealp{2012SoPh..275...17L}) on board the Solar Dynamics Observatory
(SDO, \citealp{2012SoPh..275....3P}), that time-series of coronal emission
may be better described by other models.  These models, {\bf based
  around \PL\ Fourier \PS}, have implications for the practice of
coronal seismology, and may be indicative of the nature of the
fundamental energy deposition that keeps the corona hot.

@@

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
The first contribution to both models $M_{1}$ and $M_{2}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all {\bf similar} parts of the solar
atmosphere {\bf , that is quiet Sun, moss, loop footpoints and above
  sunspots}.  Further, \cite{2014AA...563A...8A} show that a
\PL\ \PS\ is present in coronal active region and quiet Sun
time-series over the frequency range 0.01 - 1 mHz, overlapping with
the frequency studied in this paper.
